Rapid cycleway prioritisation tool

### 2020-06-01 code/index.Rmd
Fix typos in index

Please provide feedback on these preliminary results on this [web form (estimated time to complete: 5 minutes)](https://urldefense.proofpoint.com/v2/url?u=https-3A__forms.office.com_Pages_ResponsePage.aspx-3Fid-3DqO3qvR3IzkWGPlIypTW3y9orQ9urif9IgBaXiRS9eEpUM0JCTDRFTTEwSDRVMUs0VVhVWEdGRDA3RS4u&d=DwMCaQ&c=troKkvwivNn_CddsvWCHHPiPoFoTgTGIbXJULvYU158&r=DXeEYtdSYDBZN2DBwEgAHMmX5PQ_ob9r2MynFWta2mU&m=mkyUa3RIC9d5LSrHUqk_WdstQR1OQuTWyYLBecHFMm0&s=dD7GVcQbjZ2AcdCObSe-rNKmLLDBhu98ChFupIIrlJA&e=).

@@

The focus is on roads the either have a spare lane or that have an estimated width of above 10 m, *and* high cycling potential.
The 10 m width is an indicator of road conditions and larger widths, of 15+ m, may be required for road space reallocation without other changes such as making roads one way for motor traffic or removing central markings as described in , depending on factors such as on street parking levels.
The work is based evidence that road space can be reallocated without causing congestion at a time when traffic levels, particularly during the rush hours, are greatly reduced.

@@

@@

If you find any other issues with the results or have suggestions of ways to improve the results, please provide feedback on the [web form](https://urldefense.proofpoint.com/v2/url?u=https-3A__forms.office.com_Pages_ResponsePage.aspx-3Fid-3DqO3qvR3IzkWGPlIypTW3y9orQ9urif9IgBaXiRS9eEpUM0JCTDRFTTEwSDRVMUs0VVhVWEdGRDA3RS4u&d=DwMCaQ&c=troKkvwivNn_CddsvWCHHPiPoFoTgTGIbXJULvYU158&r=DXeEYtdSYDBZN2DBwEgAHMmX5PQ_ob9r2MynFWta2mU&m=mkyUa3RIC9d5LSrHUqk_WdstQR1OQuTWyYLBecHFMm0&s=dD7GVcQbjZ2AcdCObSe-rNKmLLDBhu98ChFupIIrlJA&e=).
If you are interested in the code underlying the project and would like to support the project with technical input, please provide feedback via the [GitHub issue tracker (requires a GitHub account)](https://github.com/cyipt/popupCycleways/issues).

>>>>

Please provide feedback on these preliminary results on this [web form (estimated time to complete: 5 minutes)](https://forms.office.com/Pages/ResponsePage.aspx?id=qO3qvR3IzkWGPlIypTW3y9orQ9urif9IgBaXiRS9eEpUM0JCTDRFTTEwSDRVMUs0VVhVWEdGRDA3RS4u).

@@

The focus is on roads that have 'spare space' (defined as those with a spare lane or that have an estimated width of above 10 m) and high cycling potential.
The 10 m width is an indicator of road conditions and larger widths, of 15+ m, may be required for road space reallocation without other changes such as making roads one way for motor traffic or removing central markings as described in a paper by Stella Shackel and John Parkin ([2014](https://doi.org/10.1016/j.aap.2014.08.015)).
Which roads to prioritise and the most effective interventions will also depend on factors such as on street parking levels not present in the analysis.

@@

Overall the evidence presented in the tool is designed to encourage bold interventions where more space for active modes is most needed.
The work is based evidence that road space can be reallocated without causing congestion at a time when traffic levels, particularly during the rush hours, are greatly reduced.

@@

If you find any other issues with the results or have suggestions of ways to improve the results, please provide feedback on the [web form](https://forms.office.com/Pages/ResponsePage.aspx?id=qO3qvR3IzkWGPlIypTW3y9orQ9urif9IgBaXiRS9eEpUM0JCTDRFTTEwSDRVMUs0VVhVWEdGRDA3RS4u).
If you are interested in the code underlying the project and would like to support the project with technical input, please provide feedback via the [GitHub issue tracker (requires a GitHub account)](https://github.com/cyipt/popupCycleways/issues).
